%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Shixiong Qi} % Your name
%\address{Taibai South Road NO.2 \\ Xi'an, Shaanxi, China 710071} % Your address
%\address{(+1)~$\cdot$~951~$\cdot$~756~$\cdot$~3741 \\ qishixiong19931009@gmail.com} % Your phone number and email

\begin{document}

%\begin{rSection}{Personal Information}

%{\bf Gender}: Male\\
%{\bf Age}: 25 \\
%{\bf Birth date and place}: 10/09/1993, Nanjing, China

%\end{rSection}

\begin{rSection}{Affiliation}

{\bf Department of Computer Science and Engineering} \hfill {September 2018 - Present}\\
University of California, Riverside

{\bf State Key Laboratory of Integrated Service Networks (ISN)} \hfill {September 2015 - June 2018}\\
School of Telecommunications Engineering, Xidian University

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of California, Riverside}\\
{PhD ongoing in Computer Science}\hfill {September 2018 - Present}  \\
Overall GPA: 3.80/4\\

{\bf Xidian University}, {Xi'an, Shaanxi, China}\\
{M.S. in Communication \& Information Systems}\hfill {September 2015 - June 2018}  \\
Overall GPA: 3.71/4 (Ranking 25/284)\\


{\bf Nanjing University of Posts and Telecommunications}, {Nanjing, Jiangsu, China}\\
{B.S. in Electronic Information Engineering} \hfill {September 2011 - July 2015} \\
Overall GPA: 3.69/4 (Ranking 5/97)\\

\end{rSection}

%----------------------------------------------------------------------------------------
%	Research Interests
%----------------------------------------------------------------------------------------

\begin{rSection}{Past Research Interests}
\begin{rSubsection}{Optical interconnect network for on-chip computing system}{}{}{}
\item Topology, communication scheme and interface design for core-to-core and core-to-memory communication.
\item Design and improvement of cache coherence protocol in optical interconnect memory system.
\item Application specific memory system design, processing in memory (PIM).
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}
\begin{rSubsection}{Journal}{}{}{}

\item Lei Huang, Kun Wang, {\bf Shixiong Qi}, Huaxi Gu and Yintang Yang, "Panzer: A 6 x 6 photonic router for Optical Network," IEICE Electronics Express {\bf 21}(13), 2016, pp. 20160719 (SCI indexed).

\item Kun Wang, {\bf Shixiong Qi}, Zheng Chen, Yintang Yang, Huaxi Gu, “SMONoC: A Hierarchical Optical Network-on-Chip Using Statistical Multiplexing Strategy,” Optical Switching and Networking, Elsevier(accepted and in press, SCI indexed).

\item Jiaxiang Li, Huaxi Gu, {\bf Shixiong Qi}, Haoran Wang,and Kang Wang, “ALPHA: A Hybrid Topology for Memory-centric Network,” IEICE Electronics Express, 2019 (SCI indexed).

\end{rSubsection}

\begin{rSubsection}{Conference}{}{}{}

\item {\bf Shixiong Qi}, Huaxi Gu, Haibo Zhang, Yawen Chen, Testudo: A Low Latency and High-Efficient Memory-Centric Network Using Optical Interconnect, Globecom 2017.

\item {\bf Shixiong Qi}, Kun Wang, Huaxi Gu, Kang Wang, Xiaolu Wang, "Crosstalk Analysis for Closed Ring-Based Optical Network-on-Chip," 2015 International Conference on Communication Problem-solving (ICCP2015), pp.331-333. 

\item Lei Huang, {\bf Shixiong Qi}, Kun Wang, Huaxi Gu, "LACE: A Non-Blocking On-Chip Optical Router by Utilizing the Wavelength Routing Technology," 2017 16th International Conference on Optical Communications and Networks (ICOCN). IEEE, 2017.
\item Xinglong Diao, Lei Huang, Wei Tan, {\bf Shixiong Qi}, Huaxi Gu, "A Low-Crosstalk Optical Router Using Multi-Layer Coupled MR for ONoC," 2017 16th International Conference on Optical Communications and Networks (ICOCN). IEEE, 2017.

\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%   P.R.C. Patent
%----------------------------------------------------------------------------------------
\begin{rSection}{P.R.C. Patent}
\begin{rSubsection}{}{}{}{}

\item Kun Wang, {\bf Shixiong Qi}, Zheng Chen, Huaxi Gu, Yintang Yang, Long Zhao. An Optical Network-on-Chip System and Communication Scheme based on Statistical Multiplexing Strategy. 2016-03. Application No.201610165497.1
\item Lei Huang, Kun Wang, Huaxi Gu, Yintang Yang, {\bf Shixiong Qi}, Wei Tan. A Multi-port Scalable On-chip Optical Router Supporting Multicast Communication. 2016-05. Application No.201610312528.1

\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%   Submitted papers
%----------------------------------------------------------------------------------------
%\begin{rSection}{Submitted papers}
%\begin{rSubsection}{}{}{}{}

%\item Kun Wang, {\bf Shixiong Qi}, Zheng Chen, Yintang Yang, Huaxi Gu, SMONoC: A Hierarchical Optical Network-on-Chip Using Statistical Multiplexing Strategy, Submitted to Optics Communications.

%\end{rSubsection}
%\end{rSection}

%----------------------------------------------------------------------------------------
%   Honours and awards
%----------------------------------------------------------------------------------------
\begin{rSection}{Honours and awards}
\begin{rSubsection}{}{}{}{}

\item Second-class scholarship, Nanjing University of Posts and Telecommunications \hfill {2012, 2013, 2014}
\item Excellent Student Award, Nanjing University of Posts and Telecommunications \hfill {2013}
\item First Prize in Jiangsu Province, the National Mathematical Modeling Contest \hfill {2013}
\item Honorable Mention, Mathematical Contest In Modeling \hfill {2014}
\item First-class scholarship, Xidian Univertsity \hfill {2015}
\item Second-class scholarship, Xidian Univertsity \hfill {2016}
\item Excellent Student Award, Xidian University \hfill {2016}
\item National scholarship, Xidian University (Top 3\% of 700+) \hfill {2017}
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%-----------------------------------------------------------------------------------------
\begin{rSubsection}{Xidian University}{August 2015 - June 2018}{Research assistant}{Xi'an, China}
\item Lead the application for the Opening Foundation of State Key Laboratory of Computer Science by Institute of Computing Technology, Chinese Academy of Sciences.
\item Take part in the application for National Natural Science Foundation of China as the main participant.
\item Develop the simulation platform for optically connected memory system based on OMNET++ simulator.
\item Design interconnection network for the communication between cores and Hybrid Memory Cube (HMC) by using optical interconnect technology, including the topology, the communication method and the network interface.
\item Research on the design and improvement of cache coherence protocol in optical interconnect memory system.
\item Research on the design of on-chip optical router with high scalability.
\item Arrange the visiting activity for Prof. P. Pande, Professor in Washington State University.
\item Serve as the teaching assistant (TA) in Switching Principle and Technology (Autumn 2016) and Communication Networks Theory (Spring 2017).
\end{rSubsection}

\begin{rSubsection}{University of Otago}{August 2017}{Visiting Student}{Dunedin, New Zealand}

\item Research on efficient design on Optical Network-on-Chips.
\item Develop a C++ based simulator for testing the on-chip multicast communication algorithm, which can realize non-blocking multicast communication between different cores.

\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Technical Strengths}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Programming Languages & C++ \\
%Knowledge & Communication networks theory, \\
% & Information theory, \\
% & Cache coherence protocol, \\
% & Memory system architecture, \\
% & Principe of interconnection network, \\
% & Optical interconnect \\
%Simulation software & OMNET++, Booksim 2.0, Gem5, DRAMSim2, \\
%&OPNET 14.5, Netrace, Hotspot 5.0 \\
%Operating systems & Windows, Linux(Ubuntu) \\
%\end{tabular}

%\end{rSection}

%\begin{rSection}{Languages}
%Native: Chinese\\
%English: Fluent\\
%\end{rSection}

%\begin{rSection}{Travel History}
%New Zealand (2017)
%\end{rSection}

%----------------------------------------------------------------------------------------
%	Referees
%----------------------------------------------------------------------------------------
\begin{rSection}{Referees}
%{\bf My supervisors}: \\
Prof. Huaxi Gu \\
State Key Laboratory of Integrated Service Networks, Xidian University \\
Email: hxgu@xidian.edu.cn\\

Dr. Yawen Chen \\
Department of Computer Science, University of Otago \\
Email: yawen@cs.otago.ac.nz 


\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
